Below-ground sink limitation alters growth and carbon balance of Eucalyptus seedlings

### 2015-11-13 manuscript/manuscript_pve.Rmd
spelling

\
Increasing rates of non-leaf respiration (M~S2~) improved biomass predictions but to a far lesser extent than changes to leaf C allocation. We also show that very large increases in non-leaf respiration rates would have been required to accurately predict observed seedling biomass. Although the fraction of photosynthate used in respiration is known to vary among species and is sensitive to changes in growth rates [@Lambers2008], results from M~S2~ highlight a lack of knowledge regarding how respiration rates of individual tissues, within a single plant, maybe be differentially affected by environmental change. This is noteworthy, as C balance is a delicate equilibrium between fluxes of A and respiration, partial accounting of C dynamics can easily lead to erroneous conclusions (Valentini et al. 2000). These results infer that using fixed rates of respiration in models likely underestimates plant responses to sink limitation. Thus, we agree with Delucia et al. [-@delucia2007forest] that it is likely inappropriate to assume that respiration is a constant fraction of gross primary production in models. Our findings reveal that a combination of different mechanisms, beyond A, are likely at play in driving the observed seedling biomass response to sink manipulation. However, the degree to which these mechanisms will regulate a growth will undoubtedly shift across different experimental manipulations and plant species.

>>>>

\
Increasing rates of non-leaf respiration (M~S2~) improved biomass predictions but to a far lesser extent than changes to leaf C allocation. We also show that very large increases in non-leaf respiration rates would have been required to accurately predict observed seedling biomass. Although the fraction of photosynthate used in respiration is known to vary among species and is sensitive to changes in growth rates [@Lambers2008], results from M~S2~ highlight a lack of knowledge regarding how respiration rates of individual tissues, within a single plant, maybe be differentially affected by environmental change. This is noteworthy, as C balance is a delicate equilibrium between fluxes of A and respiration, partial accounting of C dynamics can easily lead to erroneous conclusions (Valentini et al. 2000). These results infer that using fixed rates of respiration in models likely underestimates plant responses to sink limitation. Thus, we agree with Delucia et al. [-@delucia2007forest] that it is likely inappropriate to assume that respiration is a constant fraction of gross primary production in models. Our findings reveal that a combination of different mechanisms, beyond A, are likely at play in driving the observed seedling biomass response to sink manipulation. However, the degree to which these mechanisms will regulate growth will undoubtedly shift across different experimental manipulations and plant species.
